Effect of character correlation

### 2018-03-27 Analysis/02-EffectCorrelationFullResults.Rmd
added the looooong tables

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_summary <- paste0("Full_Tab_Summary", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1], path = "../Writing/Tables/")
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2], path = "../Writing/Tables/")
make.xtable(sum_RF_null, caption = captions_summary[3], label = labels_summary[3], path = "../Writing/Tables/")
make.xtable(sum_Tr_null, caption = captions_summary[4], label = labels_summary[4], path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_bc <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

@@

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_wx <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

>>>>

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide'}
## Labels
labels_summary <- paste0("Full_Tab_Summary", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1], path = "../Writing/Tables/", longtable = TRUE)
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2], path = "../Writing/Tables/", longtable = TRUE)
make.xtable(sum_RF_null, caption = captions_summary[3], label = labels_summary[3], path = "../Writing/Tables/", longtable = TRUE)
make.xtable(sum_Tr_null, caption = captions_summary[4], label = labels_summary[4], path = "../Writing/Tables/", longtable = TRUE)
```

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide'}
## Labels
labels_bc <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide'}
## Labels
labels_wx <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))
